### 2013-07-05 tests_Kinematics.Rmd
added regularization + parameter testing
some Kinematic results

>>>>

########################################################
# Lambda Test
lambda.values <- seq(0.5,0.999,length.out=20)
n.runs <- 5

source("gapolyfuncs.R")
errors <- test.lambda(my.data, lambda.values, runs=n.runs, population=50, iterations=25)

df <- data.frame(error = as.vector(matrix(errors,nrow=1)),
                 lambda = as.factor(rep(round(lambda.values,3), each=n.runs)))

write.table(df, "lambda.errors.kinematics.txt")

library(ggplot2)
qplot(lambda,error,data=df,geom=c("jitter","boxplot")) + 
  ylab("root-mean-square error") + 
  xlab("lambda value") +
 # coord_cartesian(ylim = c(0, 50))  +
  ggtitle("Kinematics dataset")

########################################################
